An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-02 poly-embed-journal/poly-embed-journal.tex
pass over sec 3

\raf{We should probably add the type of $\ell$ and $L$ in each lemma/prop/thm statement, or add something like: ``throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^Y$ and $L:\reals^d\to\reals^\Y$''.}

\begin{proposition}\label{prop:embed-bayes-risks}
  Let discrete loss $\ell$ be given.
  Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{I'm going ahead with the proposed definition regarding $S$, since I think we can't avoid that for this result at least.}
  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:S\to\reals^d$.
  Since $\Sc$ is representative, for all $p\in\simplex$ we have $\Sc \cap \gamma(p) \neq \emptyset$.
  \raf{Can we remove $\gamma'$ and show more directly that $\U$ is representative for $\Gamma$?  We only use the second part of Lemma~\ref{lem:loss-restrict} anyway.}
  Take $\U := \varphi(\Sc)$, and consider $\Sc$ is representative of $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
  Therefore, we have $\U$ representative of $L|_\U$ since $\Gamma(p)$ is nonempty, and $\U$ is representative of $L$.
%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~,
  \end{equation*}
  for all $p\in\simplex$.
  Moreover, the risks are polyhedral as $\risk{\ell}$ is the pointwise max of a finite set of linear functions.

@@

\jessiet{Can remove this; took the part of the proof used in Thm 2 and moved there.  It's not a dependency anywhere else.}
\raft{Oh, saw this last: didn't realize ``this'' meant the proposition (right?).  If so maybe we should demote the proposition to a corollary or just an observation.}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  \raft{Don't need power diagrams here either.  Also, I think once we have a nice clean proof of Proposition~\ref{prop:embed-bayes-risks} we can resolve the redundancy of these proofs easily, perhaps by proving the stronger statement in Proposition~\ref{prop:embed-bayes-risks}.}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  \proposedadd{Form the set $\Sc$ by iterating over the facets of $E_L$, the epigraph of $-\risk{L}$.
  For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

We extend Theorem~\ref{thm:aurenhammer} to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.

@@

\begin{lemma}
	\label{lem:poly-loss-poly-risk}
	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
	For each $U\in \U$, select $u_U \in U$, and let $\Sc' = \{u_U : U \in\U\}$.
	$\Sc$ is representative of $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
\end{proof}

@@

\jessiet{New to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.

>>>>

\raf{We should probably add the type of $\ell$ and $L$ in each lemma/prop/thm statement, or add something like: ``throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ and $L:\reals^d\to\reals^\Y$''.}

\begin{proposition}\label{prop:embed-bayes-risks}
  Let discrete loss $\ell$ be given.
  Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{4/2/2021 first part of the proof should be done now.}
  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:S\to\reals^d$.
  By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$.
  Since $\Sc$ is representative for $\ell$, for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
  In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, so $\U$ is representative for $L$.
  \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.  I'm thinking we should expand on this perspective in section 5, maybe introduce a notion of equivalence between any two losses (discrete or otherwise), and define trim in that context.}
  % Taking $\U := \varphi(\Sc)$, we have that $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we have $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), for all $p\in\simplex$ we have
  \begin{equation*}
    \risk{\ell}(p) = \risk{\ell|_\Sc}(p) = \min_{r \in \Sc}\inprod{p}{\ell(r)} = \min_{r \in \Sc}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~.
  \end{equation*}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  \proposedadd{Form the set $\Sc$ by iterating over the facets of $E_L$, the epigraph of $-\risk{L}$.
  For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

\raf{Here's what I'm thinking for the text from here to Lemma~\ref{lem:poly-loss-poly-risk} (let's not implement just yet though): Let's move Lemma~\ref{lem:polyhedral-pd-same} to the appendix, and state Lemma~\ref{lem:polyhedral-range-gamma} but move the proof to the appendix.  Then we can keep the proof of Lemma~\ref{lem:poly-loss-poly-risk}.}
We extend Theorem~\ref{thm:aurenhammer} to a weighted sum of convex functions, showing that the induced power diagram is the same for any choice of strictly positive weights.

@@

\begin{lemma}
	\label{lem:poly-loss-poly-risk}
	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
	For each $U\in \U$, select $u_U \in U$, and let $\Sc' = \{u_U : U \in\U\}$.
	$\Sc$ is representative of $L$\raft{let's use ``representative for'' to be consistent; can always find/replace to change later \#burn}, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
\end{proof}

@@

\jessiet{New to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}\raft{Ah, good call! \#burn}.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider the embedding $\varphi$ given by the property embedding and take the discrete loss $\ell:r \mapsto L(\varphi(r))$.
	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$, and the risks being polyhedral follows from $\ell$ being discrete.
